---
title: "chp5 ex7"
author: "kwon"
date: "2018년 8월 13일"
output: html_document
---

#7
In Sections 5.3.2 and 5.3.3, we saw that the cv.glm() function can be
used in order to compute the LOOCV test error estimate. Alternatively,
one could compute those quantities using just the glm() and predict.glm() functions, and a for loop. You will now take this approach
in order to compute the LOOCV error for a simple logistic
regression model on the Weekly data set. Recall that in the context
of classification problems, the LOOCV error is given in (5.4).
\
##(a) Fit a logistic regressionmodel that predicts Direction using Lag1
and Lag2.
```{r}
require(ISLR)
n = length(Weekly[,1])
glm(Direction~Lag1+Lag2, data= Weekly, family="binomial")
```


##(b) Fit a logistic regressionmodel that predicts Direction using Lag1
and Lag2 using all but the first observation.
```{r}
logit1 = glm(Direction~Lag1+Lag2, data= Weekly[2:n,], family="binomial")
```

##(c) Use the model from (b) to predict the direction of the first observation.
You can do this by predicting that the first observation
will go up if P(Direction="Up"|Lag1, Lag2) > 0.5. Was this observation
correctly classified?
```{r}
prob = predict(logit1, Weekly[1,], type="response")
contrasts (Weekly$Direction)
prob>0.5
Weekly[1,]$Direction
```
The model predicted Up, while the actual data is "Down"

(d) Write a for loop from i = 1 to i = n, where n is the number of
observations in the data set, that performs each of the following
steps:
i. Fit a logistic regression model using all but the ith observation
to predict Direction using Lag1 and Lag2.

\
ii. Compute the posterior probability of the market moving up
for the ith observation.
/
iii. Use the posterior probability for the ith observation in order
to predict whether or not the market moves up.
/
iv. Determine whether or not an error was made in predicting
the direction for the ith observation. If an error was made,
then indicate this as a 1, and otherwise indicate it as a 0.

```{r}
count = rep(0, n)
for(i in 1:n){
  temp_model = glm(Direction~Lag1+Lag2, data=Weekly[-i,], family="binomial")
  prob = predict(temp_model, Weekly[i,], type="response")
  pred = if(prob>0.5) "Up" else "Down"
  count[i] = (pred== Weekly[i,]$Direction)
}
```

(e) Take the average of the n numbers obtained in (d)iv in order to
obtain the LOOCV estimate for the test error. Comment on the
results.
```{r}
mean(count)
```
The average test error rate of LOOCV is about 45%.

