---
title: "chp5 ex6"
author: "kwon"
date: "2018년 8월 13일"
output: html_document
---

#6 
We continue to consider the use of a logistic regression model to
predict the probability of default using income and balance on the
Default data set. In particular, we will now compute estimates for
the standard errors of the income and balance logistic regression coefficients
in two different ways: (1) using the bootstrap, and (2) using
the standard formula for computing the standard errors in the glm()
function. Do not forget to set a random seed before beginning your
analysis.
\
##(a) Using the summary() and glm() functions, determine the estimated
standard errors for the coefficients associated with income
and balance in a multiple logistic regression model that uses
both predictors.
```{r}
set.seed(1)
def_logit = glm(default~income+balance, data= Default, family="binomial")
summary(def_logit)
```

##(b) Write a function, boot.fn(), that takes as input the Default data
set as well as an index of the observations, and that outputs
the coefficient estimates for income and balance in the multiple
logistic regression model.
```{r}
boot.fn = function(data, index){
  def_boot = glm(default~income+balance, data= data, subset = index, family="binomial")
  return(coef(def_boot))
}
```

##(c) Use the boot() function together with your boot.fn() function to
estimate the standard errors of the logistic regression coefficients
for income and balance.
```{r}
boot(Default, boot.fn, R=1000)
```

##(d) Comment on the estimated standard errors obtained using the
glm() function and using your bootstrap function.
```{r}
summary(def_logit)$coef[,"Std. Error"]
```
Both results are very close to two decimals.
