---
title: "chp5 ex concept"
author: "kwon"
date: "2018년 8월 13일"
output: html_document
---

# 1

Using the following rules:

$$ Var(X+Y) = Var(X) + Var(Y) + 2 Cov(X,Y) \\
\ Var(cX) = c^2 Var(X) \ Cov(cX,Y) = Cov(X,cY) = c Cov(X,Y) $$

Minimizing two-asset financial portfolio: $$ Var(\alpha X + (1 - \alpha)Y) \ = Var(\alpha X) + Var((1 - \alpha) Y) + 2 Cov(\alpha X, (1 - \alpha) Y) 
\\ = \alpha^2 Var(X) + (1 - \alpha)^2 Var(Y) + 2 \alpha (1 - \alpha) Cov(X, Y) \ 
\\ = \sigma_X^2 \alpha^2 + \sigma_Y^2 (1 - \alpha)^2 + 2 \sigma_{XY} (-\alpha^2 + \alpha) $$


Take the first derivative to find critical points: $$ 0 = \frac {d} {d\alpha} f(\alpha) \
\\ = 2 \sigma_X^2 \alpha + 2 \sigma_Y^2 (1 - \alpha) (-1) + 2 \sigma_{XY} (-2 \alpha + 1) \ 
\\ = \sigma_X^2 \alpha + \sigma_Y^2 (\alpha - 1) + \sigma_{XY} (-2 \alpha + 1) 
\\= (\sigma_X^2 + \sigma_Y^2 - 2 \sigma_{XY}) \alpha - \sigma_Y^2 + \sigma_{XY} \
\\ \alpha = \frac {\sigma_Y^2 - \sigma_{XY}} {\sigma_X^2 + \sigma_Y^2 - 2 \sigma_{XY}} $$

#2
## a
$1 - 1/n$

## b
$1 - 1/n$

## c
Each bootstrap sampling has 1/n chance of sampling jth observation, which is independet from each others. Thus, $ (1-1/n)^n$ is the probability of not sampling jth observation.

## d
1-1/5

## e
1-1/100

## f
1-1/10,000

## g
```{r}
pr = function(n) return(1 - (1 - 1/n)^n)
x = 1:100000
plot(x, pr(x))
```

## h
```{r}
store = rep(NA, 10000)
for(i in 1:10000){
  store[i] = sum(sample(1:100, rep=TRUE)==4)>0
}
mean(store)
```
It shows same results from the above bootstrap sampling.

#3
##a
Divide data into k folds, and leave one fold for test data, while use others for training. Repeat this process k times, changing test data from each folds.

##b
###i
+: CV has relatively low variance, as vaildation set apporach highly depends on observations. And, it uses more data for training, while validation set overestimates the test error.
\
-: CV is relatively hard to implement.

###ii
+: It is computationally faster.
\
-: Higher bias, and lower variance than LOOCV.

# 4
We can estimate the standard deviation of our prediction by using bootstrap method. Bootstrap is sampling from data for n times. For each sampling, fit a new model and obtain the estimate. 








