---
title: "chp5 ex8"
author: "kwon"
date: "2018년 8월 13일"
output: html_document
---
#8
We will now perform cross-validation on a simulated data set.

##(a) Generate a simulated data set as follows:
```{r}
set.seed (1)
x=rnorm (100)
y=x-2* x^2+ rnorm (100)
```
In this data set, what is n and what is p? Write out the model
used to generate the data in equation form.
/
n is 100, while p is 2.

##(b) Create a scatterplot of X against Y . Comment on what you find.
```{r}
plot(x,y)
```
Looks like it has quadratic form.

/
(c) Set a random seed, and then compute the LOOCV errors that
result from fitting the following four models using least squares:
i. Y = β0 + β1X +  \
ii. Y = β0 + β1X + β2X2 +  \
iii. Y = β0 + β1X + β2X2 + β3X3 +  \
iv. Y = β0 + β1X + β2X2 + β3X3 + β4X4 + . \
Note you may find it helpful to use the data.frame() function
to create a single data set containing both X and Y .
```{r}
set.seed(1)
test_data = data.frame(Y=y, X=x)

library (boot)
cv.error=rep (0,4)
for (i in 1:4){
  glm.fit=glm(Y~poly(X ,i),data= test_data)
  cv.error[i]=cv.glm(test_data ,glm.fit)$delta [1]
}
cv.error

```


\
##(d) Repeat (c) using another random seed, and report your results.
Are your results the same as what you got in (c)? Why?
```{r}
set.seed(2)
test_data = data.frame(Y=y, X=x)

library (boot)
cv.error=rep (0,4)
for (i in 1:4){
  glm.fit=glm(Y~poly(X ,i),data= test_data)
  cv.error[i]=cv.glm(test_data ,glm.fit)$delta [1]
}
cv.error

```
It is same as above result, that is there only one way of calculating LOOCV.

\
(e) Which of the models in (c) had the smallest LOOCV error? Is
this what you expected? Explain your answer. \
The model with second order polynomial. It matches with the true model.

\
(f) Comment on the statistical significance of the coefficient estimates
that results from fitting each of the models in (c) using
least squares. Do these results agree with the conclusions drawn
based on the cross-validation results?
```{r}
summary(glm.fit)
```
It agrees with true model where first order, and second order shows significant p-values.



