---
title: "chp5 ex9"
author: "kwon"
date: "2018년 8월 14일"
output: html_document
---
#9 
We will now consider the Boston housing data set, from the MASS
library.
##(a) Based on this data set, provide an estimate for the population
mean of medv. Call this estimate ˆμ.
```{r}
require(MASS)
mean(Boston$medv)
```

\
(b) Provide an estimate of the standard error of ˆμ. Interpret this
result.
Hint: We can compute the standard error of the sample mean by
dividing the sample standard deviation by the square root of the
number of observations.
```{r}
sd(Boston$medv)/sqrt(length(Boston$medv))
```

\
(c) Now estimate the standard error of ˆμ using the bootstrap. How
does this compare to your answer from (b)?
```{r}
require(boot)
boot.fn = function(data, index){
  return(mean(data[index]))
}

bootstrp = boot(Boston$medv, boot.fn, 1000)
bootstrp
```
Both results are very close.

\
(d) Based on your bootstrap estimate from (c), provide a 95% confidence
interval for the mean of medv. Compare it to the results
obtained using t.test(Boston$medv).
Hint: You can approximate a 95% confidence interval using the
formula [ˆμ − 2SE(ˆμ), ˆμ + 2SE(ˆμ)].
```{r}
c(bootstrp$t0 - 2*0.4129857, bootstrp$t0 + 2*0.4129857)
t.test(Boston$medv)
```
Bootstrap results are only about 0.02 away from the t-estimate.

\
(e) Based on this data set, provide an estimate, ˆμmed, for the median
value of medv in the population.
```{r}
median(Boston$medv)
boot.med = function(data, index){
  return(median(data[index]))
}
boot_med = boot(Boston$medv, boot.med, 1000)
boot_med
```
Median 21.2 with standard error of 0.39.

\
(f) We now would like to estimate the standard error of ˆμmed. Unfortunately,
there is no simple formula for computing the standard
error of the median. Instead, estimate the standard error of the
median using the bootstrap. Comment on your findings. \
Result is on (e).

\
(g) Based on this data set, provide an estimate for the tenth percentile
of medv in Boston suburbs. Call this quantity ˆμ0.1. (You
can use the quantile() function.)
```{r}
quantile(Boston$medv, 0.1)
boot.q10 = function(data,index){
  return(quantile(data[index], 0.1))
}
boot_q10 = boot(Boston$medv, boot.q10, 1000)
boot_q10
```

\
(h) Use the bootstrap to estimate the standard error of ˆμ0.1. Comment
on your findings. \
Tenth-quantile is 12.75 with standard error 0.498, which seems relatively small to the value.








