---
title: "chp4 ex12"
author: "kwon"
date: "2018년 8월 10일"
output: html_document
---
# 12
(**a**) Write a function, Power(), that prints out the result of raising 2
to the 3rd power. In other words, your function should compute
23 and print out the results.
Hint: Recall that x^a raises x to the power a. Use the print()
function to output the result.
```{r}
Power <- function(x,a){
  print(x^a)
}
```

\
(**b**) Create a new function, Power2(), that allows you to pass any
two numbers, x and a, and prints out the value of x^a. You can
do this by beginning your function with the line
Power2 =function (x,a){
You should be able to call your function by entering, for instance,
Power2 (3,8)
on the command line. This should output the value of 3^8, namely,
6, 561.
```{r}
Power(3,8)
```

\
(c) Using the Power2() function that you just wrote, compute 10^3,
8^17, and 131^3.
```{r}
Power(10,3)
Power(8,17)
Power(131,3)
```
\
(d) Now create a new function, Power3(), that actually returns the
result x^a as an R object, rather than simply printing it to the
screen. That is, if you store the value x^a in an object called
result within your function, then you can simply return() this
return()
result, using the following line:
return (result )
The line above should be the last line in your function, before
the } symbol.
```{r}
Power3 <- function(x,a){  
  result =x^a
  return(result)
}
```

(e) Now using the Power3() function, create a plot of f(x) = x2.
The x-axis should display a range of integers from 1 to 10, and
the y-axis should display x2. Label the axes appropriately, and
use an appropriate title for the figure. Consider displaying either
the x-axis, the y-axis, or both on the log-scale. You can do this
by using log=‘‘x’’, log=‘‘y’’, or log=‘‘xy’’ as arguments to
the plot() function.
```{r}
x = 1:10
plot(x, Power3(x,2), log="xy")
```

(f) Create a function, PlotPower(), that allows you to create a plot
of x against x^a for a fixed a and for a range of values of x. For
instance, if you call
PlotPower (1:10 ,3)
then a plot should be created with an x-axis taking on values
1, 2, . . . , 10, and a y-axis taking on values 13, 23, . . . , 103.
```{r}
PlotPower <- function(x,a){
  plot(x, Power3(x,a))
}
PlotPower(1:10,3)
```